---
title: "EEG analysis"
output: html_notebook
---

imports
```{r}
library(tidyr)
library(purrr)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(reshape2)
```

load data
```{r}
inexp_meditation_files = sort(list.files("ffted/",pattern="^0_ffted_med"))
inexp_reference_files = sort(list.files("ffted/",pattern="^0_ffted_ref"))
exp_meditation_files = sort(list.files("ffted/",pattern="^1_ffted_med"))
exp_reference_files = sort(list.files("ffted/",pattern="^1_ffted_ref"))


exp_meditation = list()
for(i in 1:length(exp_meditation_files)) {
  file = exp_meditation_files[i]
  exp_meditation[[i]] <-  read.csv(paste("ffted/", file, sep=""))
  exp_meditation[[i]] <- exp_meditation[[i]][rowSums(exp_meditation[[i]] == "-Inf") == 0, , drop = FALSE]
}

inexp_meditation = list()
for(i in 1:length(inexp_meditation_files)) {
  file = inexp_meditation_files[i]
  inexp_meditation[[i]] <-  read.csv(paste("ffted/", file, sep=""))
  inexp_meditation[[i]] <- inexp_meditation[[i]][rowSums(inexp_meditation[[i]] == "-Inf") == 0, , drop = FALSE]
}

exp_reference = list()
for(i in 1:length(exp_reference_files)) {
  file = exp_reference_files[i]
  exp_reference[[i]] <-  read.csv(paste("ffted/", file, sep=""))
  exp_reference[[i]] <- exp_reference[[i]][rowSums(exp_reference[[i]] == "-Inf") == 0, , drop = FALSE]
}

inexp_reference = list()
for(i in 1:length(inexp_reference_files)) {
  file = inexp_reference_files[i]
  inexp_reference[[i]] <-  read.csv(paste("ffted/", file, sep=""))
  inexp_reference[[i]] <- inexp_reference[[i]][rowSums(inexp_reference[[i]] == "-Inf") == 0, , drop = FALSE]
}
```


subsetting data
```{r}
subset_and_melt <- function(med, exp, wave, electrodes, melt, melt_all){
  if(med){
    if(exp){
      df <- exp_meditation
    }
    else{
      df <- inexp_meditation
    }
  }
  else{
    if(exp){
      df <- exp_reference
    }
    else{
      df <- inexp_reference
    }
  }

  data = list()
  for(i in 1:length(df)) {
  data[[i]] <- df[[i]][, grepl(paste('(', wave, ')|(', electrodes, ')|(timestamp)', sep = ""), names(df[[i]]))]
  if(melt){
    data[[i]] <- melt(data[[i]], id.vars = 'timestamps', variable.name = 'waves')
    data[[i]]$waves <- as.factor(data[[i]]$waves)
  }
  }
  if(melt_all){
    data <- melt(data, id.vars = c('timestamps', 'waves', 'value'))
    data$L1 <- as.factor(data$L1)
  }
  
  return(data)
}
```

testing
```{r}
temp_2 <- subset_and_melt(FALSE, TRUE, "beta", "None", TRUE, TRUE)
#ggplot(temp_2[[1]], aes(timestamps,value)) + geom_line(aes(colour = waves))
```

things to think about:
* extreme points, spikes, etc
* different smoothing rate
* difference between meditative and regular state
* difference between experienced meditators and newbies
* how to determine the levels and scale it for others
* what happens when meditation is stable
* explore the coherence between alpha and theta waves


explore experienced/inexperienced distributions of alpha wave
```{r}
alpha_exp_med = subset_and_melt(TRUE, TRUE, 'alpha', 'ALL', TRUE, TRUE)
alpha_inexp_med = subset_and_melt(TRUE, FALSE, 'alpha', 'ALL', TRUE, TRUE)
alpha_exp_med$exp <- "experienced"
alpha_exp_med$exp <- as.factor(alpha_exp_med$exp)
alpha_inexp_med$exp <- "inexperienced"
alpha_inexp_med$exp <- as.factor(alpha_inexp_med$exp)
temp <- rbind(alpha_exp_med, alpha_inexp_med)
ggplot(temp, aes(value, fill = exp)) + 
  geom_histogram(alpha = 0.5, bins = 100, position = 'identity')
```

explore experienced/inexperienced distributions of theta wave
```{r}
theta_exp_med = subset_and_melt(TRUE, TRUE, 'theta', 'ALL', TRUE, TRUE)
theta_inexp_med = subset_and_melt(TRUE, FALSE, 'theta', 'ALL', TRUE, TRUE)
theta_exp_med$exp <- "experienced"
theta_exp_med$exp <- as.factor(theta_exp_med$exp)
theta_inexp_med$exp <- "inexperienced"
theta_inexp_med$exp <- as.factor(theta_inexp_med$exp)
temp <- rbind(theta_exp_med, theta_inexp_med)
ggplot(temp, aes(value, fill = exp)) + 
  geom_histogram(alpha = 0.5, bins = 100, position = 'identity')
```

explore experienced/inexperienced distributions of beta wave
```{r}
beta_exp_med = subset_and_melt(TRUE, TRUE, 'beta', 'ALL', TRUE, TRUE)
beta_inexp_med = subset_and_melt(TRUE, FALSE, 'beta', 'ALL', TRUE, TRUE)
beta_exp_med$exp <- "experienced"
beta_exp_med$exp <- as.factor(beta_exp_med$exp)
beta_inexp_med$exp <- "inexperienced"
beta_inexp_med$exp <- as.factor(beta_inexp_med$exp)
temp <- rbind(beta_exp_med, beta_inexp_med)
ggplot(temp, aes(value, fill = exp)) + 
  geom_histogram(alpha = 0.5, bins = 100, position = 'identity')
```

explore experienced/inexperienced distributions of gamma wave
```{r}
gamma_exp_med = subset_and_melt(TRUE, TRUE, 'gamma', 'ALL', TRUE, TRUE)
gamma_inexp_med = subset_and_melt(TRUE, FALSE, 'gamma', 'ALL', TRUE, TRUE)
gamma_exp_med$exp <- "experienced"
gamma_exp_med$exp <- as.factor(gamma_exp_med$exp)
gamma_inexp_med$exp <- "inexperienced"
gamma_inexp_med$exp <- as.factor(gamma_inexp_med$exp)
temp <- rbind(gamma_exp_med, gamma_inexp_med)
ggplot(temp, aes(value, fill = exp)) + 
  geom_histogram(alpha = 0.5, bins = 100, position = 'identity')
```

explore experienced/inexperienced distributions of delta wave
```{r}
delta_exp_med = subset_and_melt(TRUE, TRUE, 'delta', 'ALL', TRUE, TRUE)
delta_inexp_med = subset_and_melt(TRUE, FALSE, 'delta', 'ALL', TRUE, TRUE)
delta_exp_med$exp <- "experienced"
delta_exp_med$exp <- as.factor(delta_exp_med$exp)
delta_inexp_med$exp <- "inexperienced"
delta_inexp_med$exp <- as.factor(delta_inexp_med$exp)
temp <- rbind(delta_exp_med, delta_inexp_med)
ggplot(temp, aes(value, fill = exp)) + 
  geom_histogram(alpha = 0.5, bins = 100, position = 'identity')
```

```{r}
t.test(na.omit(alpha_exp_med$value), na.omit(alpha_inexp_med$value), var.equal = TRUE)
```


```{r}
t_test <- function(wave, med){
  wave_exp <- subset_and_melt(med, TRUE, wave, "All", TRUE, FALSE)
  medians_exp <- list()
  for(i in 1:length(wave_exp)){
    medians_exp[[i]] <- median(wave_exp[[i]]$value)
  }
  wave_inexp <- subset_and_melt(med, FALSE, wave, "All", TRUE, FALSE)
  medians_inexp <- list()
  for(i in 1:length(wave_inexp)){
    medians_inexp[[i]] <- median(wave_inexp[[i]]$value)
  }
  
  medians_exp <- unlist(medians_exp, use.names=FALSE)
  medians_inexp <- unlist(medians_inexp, use.names=FALSE)
  return(print(t.test(medians_exp, medians_inexp)))
}

```


```{r}
t_test("alpha", TRUE)
```

```{r}
a <- t_test("beta", TRUE)
```

```{r}
a <- t_test("gamma", TRUE)
```

```{r}
a <- t_test("delta", TRUE)
```

```{r}
a <- t_test("theta", TRUE)
```

There is no significant statistical difference in medians and means between experienced and
inexperienced people

```{r}
t_test_min <- function(wave, med){
  wave_exp <- subset_and_melt(med, TRUE, wave, "All", TRUE, FALSE)
  medians_exp <- list()
  for(i in 1:length(wave_exp)){
    medians_exp[[i]] <- min(wave_exp[[i]]$value)
  }
  wave_inexp <- subset_and_melt(med, FALSE, wave, "All", TRUE, FALSE)
  medians_inexp <- list()
  for(i in 1:length(wave_inexp)){
    medians_inexp[[i]] <- min(wave_inexp[[i]]$value)
  }
  
  medians_exp <- unlist(medians_exp, use.names=FALSE)
  medians_inexp <- unlist(medians_inexp, use.names=FALSE)
  return(print(t.test(medians_exp, medians_inexp)))
}
```

```{r}
a <- t_test_min("alpha", TRUE)
a <- t_test_min("theta", TRUE)
a <- t_test_min("gamma", TRUE)
a <- t_test_min("beta", TRUE)
a <- t_test_min("delta", TRUE)
```

```{r}
t_test_max <- function(wave, med){
  wave_exp <- subset_and_melt(med, TRUE, wave, "All", TRUE, FALSE)
  medians_exp <- list()
  for(i in 1:length(wave_exp)){
    medians_exp[[i]] <- max(wave_exp[[i]]$value)
  }
  wave_inexp <- subset_and_melt(med, FALSE, wave, "All", TRUE, FALSE)
  medians_inexp <- list()
  for(i in 1:length(wave_inexp)){
    medians_inexp[[i]] <- max(wave_inexp[[i]]$value)
  }
  
  medians_exp <- unlist(medians_exp, use.names=FALSE)
  medians_inexp <- unlist(medians_inexp, use.names=FALSE)
  return(print(t.test(medians_exp, medians_inexp)))
}
```

```{r}
a <- t_test_max("alpha", TRUE)
a <- t_test_max("theta", TRUE)
a <- t_test_max("gamma", TRUE)
a <- t_test_max("beta", TRUE)
a <- t_test_max("delta", TRUE)
```
```{r}
#ggplot(temp, aes(value, fill = exp)) + 
#  geom_histogram(alpha = 0.5, bins = 100, position = 'identity')

data_temp <- subset_and_melt(TRUE, TRUE, 'alpha', "ALL", TRUE, TRUE)

#geom_line(aes(y=theta_absolute_2, x = timestamps), 
#       data = without_na, color=brewer.pal(4, "Blues")[3]) + #geom_smooth(aes(y=theta_absolute_2, x = timestamps), 
#       data = without_na, color=brewer.pal(4, "Blues")[3], span = 0.01) +
```

```{r}

#temps <- data_temp[data_temp$L1 == 1 & data_temp$waves == "alpha_absolute_1", ]
# data_temp$L1 == 1,
#data_temp$waves == "alpha_absolute_1", 

#data_temp <- data_temp[data_temp$L1 == 1,]
ggplot(aes(y = value, x = timestamps), data = data_temp, data_temp$waves == "alpha_absolute_1" & data_temp$L1 ==  1) +
  geom_line()
```


